DataCamp: An Interactive Learning Tool for Programming

### 2018-04-18 manuscript.tex
updates from Weston

\hl{Weston - insert background here}
DataCamp (\url{www.datacamp.com}) was first created in X with the mission to X.
DataCamp provides a comprehensive web-based platform to interactive lessons on various coding
languages. The DataCamp website offers free `community' courses
as well as more specialized \textit{Premium} classes that require a fee. However, when used
for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
Currently, DataCamp has X number of users across X countries.

@@

@@

\hl{Weston - I can't find metadata for my course!  Is there a difference in how
data is recorded when you add members to DataCamp via email vs link via LMS?

Mine - can you add in here?
}

>>>>

\hl{Weston - insert background here}
DataCamp (\url{www.datacamp.com}) was first created in 2013 with the mission to 
``democratize data science education world wide''.
DataCamp provides a comprehensive web-based platform to interactive lessons on various coding
languages. The DataCamp website offers free `community' courses
as well as more specialized \textit{Premium} classes that require a fee. However, when used
for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
Currently, DataCamp has 2.5 million users across virtually all countries.

@@

%--------------------------------------------------------------------------------
\subsection{Builds}

Once you have executed and saved changes to your DataCamp course, DataCamp will initialize
a ``build'' attempt.  A build performs validity checks on exercises, provides
warnings and recommendations, and makes the updates available on the learning
platform.  Possible build status's include: \emph{in progress}, \emph{warning},
\emph{pass}, and \emph{fail}.  In the event that a build fails, a build log
can help you to identify the source of the error and make corrections. Warnings 
can include helpful suggestions based on design recommendations from DataCamp, 
including items such as ``The course shouldn't have more than 5 chapters'' or 
``Exercise X should have at least one submission correctness test''.

@@

In addition to tracking data on individual users, DataCamp also tracks metadata 
about the course overall.  Currently, the metadata is readily available to educators
utilizing premium courses but not to those utilizing community courses.  However,
educators utilizing community courses can correspond directly with DataCamp to 
request metadata for their course.  Metadata includes the following for each exercise
in a course:
\begin{itemize}
\item identifying information 
\item number of individuals who started the exercise
\item number of individuals who completed the exercise
\item the percent that completed the exercise
\item the percent that asked for a hint
\item the percent that asked for the solution
\end{itemize} 
This information can be used to refine and improve exercises.  A guideline
used by DataCamp is to flag and modify exercises that have exceed 20\% 
on hint or solution requests.

\hl{Mine - can you add in here?}
